### 2020-01-11 paper/paper.tex
notes to self
tweaks

% typesetting words
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\expres}{\project{\acronym{EXPRES}}}
\newcommand{\name}{\project{NameOfThis}}
\newcommand{\eprv}{\acronym{EPRV}}
\newcommand{\lfc}{\acronym{LFC}}

@@

\paragraph{Abstract:}
There have been many hardware improvements in polygonal-fiber-fed,
temperature-controlled, laser-frequency-comb or etalon-calibrated,
high-resolution, extreme-precision radial-velocity spectrographs.
Have the calibration methodologies improved to match?
Here are three relevant observations:
The first is that the calibration lines or spots from an etalon or
comb (or even arc lamp) fill the spectral range with dense calibration points.
The second is that the spectrograph lives in a stabilized,
climate-controlled environment, in which the full optical system and
detectors will only vary within a tiny range of configurations or
settings.
The third is that, given this stability, every calibration image
ever taken is relevant to every science exposure ever taken; there is
no reason to calibrate every exposure independently.
The calibration methodology we propose here---\name---addresses these
three problems by going non-parametric (no more polynomials!) and then
reducing dimensionality with a robust principal-component method.
We demonstrate the success of this method with data from the
\expres\ spectrograph.
We find... [results and so on].

@@

>>>>

% typesetting words
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\name}{\project{Excalibur}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\expres}{\project{\acronym{EXPRES}}}
\newcommand{\eprv}{\acronym{EPRV}}
\newcommand{\lfc}{\acronym{LFC}}

@@

\paragraph{Abstract:}
There have been many hardware improvements in polygonal-fiber-fed,
temperature-controlled, laser-frequency-comb or etalon-calibrated,
high-resolution, extreme-precision radial-velocity spectrographs.
Have the calibration methodologies improved to match?
Here are three relevant observations:
The first is that the calibration lines or spots from an etalon or
comb (or even arc lamp) fill the spectral range with dense calibration points.
The second is that the spectrograph lives in a stabilized,
climate-controlled environment, in which the full optical system and
detectors will only vary within a tiny range of configurations or
settings.
The third is that, given this stability, every calibration image
ever taken is relevant to every science exposure ever taken; there is
no reason to calibrate every exposure independently.
The calibration methodology we propose here---\name---addresses these
three problems by going non-parametric (no more polynomials!) and then
reducing dimensionality with a robust principal-component method.
We demonstrate the success of this method with comb and arc data
from the \expres\ spectrograph.
We find... [results and so on].

@@

HOGG: Say that there are many ways to do this, but we use PCA for now.
Note that PCA is correct in the limit that everything is very high in SNR.
